curling with hyper2 objects

### 2025-03-03 inst/curling.Rmd
typo

for(i in seq_len(ncol(curling_table))){
    x <- curling_table[,i]
    names(x) <- rownames(curling_table)
    curling2 <- curling2 + suppfun(x[!is.na(x)])
}
summary(curling2)
(curling2_maxp <- maxp(curling2))
pie(curling2_maxp)
```

>>>>

for(i in seq_len(ncol(curling_table))){
    x <- unclass(curling_table)[,i]
    names(x) <- rownames(curling_table)
    curling2 <- curling2 + suppfun(x[!is.na(x)])
}
summary(curling2)
(curling2_maxp <- maxp(curling2))
pie(curling2_maxp)
```
